Optimal (Multiway) Spatial Joins

### 2024-06-06 msj.tex
yufei

The theorem implies a recursive nature of $k$-SJ. Indeed, we will see that an $k$-SJ instance with input size $n$ and output size $\out$ can be converted to $O(k^3)$ instances of the $(k-1)$-SJ problem --- all having input size at most $n$ and output size at most $\out$ --- plus an additional cost of $O(n \log n + k \cdot \out)$ per instance. For 2-SJ, we can set $\A$  to the ``folklore algorithm'' mentioned in Section~\ref{sec:intro:prev}, which ensures $F_2(n, \out) = O(n \log n + \out)$. Combining this with \eqref{eqn:main:reccurrence} gives a recurrence that relates the time complexity of $k$-SJ to that of $(k-1)$-SJ. Solving the recurrence yields:

>>>>

The theorem implies a recursive nature of $k$-SJ. Indeed, we will see that an $k$-SJ instance with input size $n$ and output size $\out$ can be converted to $O(k^3)$ instances of the $(k-1)$-SJ problem --- all having input size at most $n$ and output size at most $\out$ --- plus an additional cost of $O(k^3) \cdot (n \log n + k \cdot \out)$. For 2-SJ, we can set $\A$  to the ``folklore algorithm'' mentioned in Section~\ref{sec:intro:prev}, which ensures $F_2(n, \out) = O(n \log n + \out)$. Combining this with \eqref{eqn:main:reccurrence} gives a recurrence that relates the time complexity of $k$-SJ to that of $(k-1)$-SJ. Solving the recurrence yields:
